\documentclass{article}
\pagestyle{empty}

\usepackage{fullpage}
\usepackage{hyperref}

\newcommand{\duphref}[1]{\href{#1}{#1}}
\newcommand{\term}[1]{\textbf{#1}}
\newcommand{\person}[1]{\textbf{#1}}

\title{Benefits of My Externship}
\author{Jeremy D.\ Frens}
\date{Fall 2006}

\begin{document}

\maketitle

\thispagestyle{empty}

\section*{Benefits to Me}

My research interests are in Programming Languages~(PL), the study of how to best express computer programs; I have also become interested in Software Engineering~(SE), the practice of actually building software solutions.  In particular, I am interested in an intersection of PL and SE: agile software development.

I am interested in agile software development in three different ways:
  \begin{itemize}
  \item in terms of its theoretical foundations,
  \item as a practical way to write sofware, and
  \item as an instructional technique.
  \end{itemize}
The last interest has resulted in some great research possibilities for me.  I am presenting a paper in March on this topic, and my sabbatical next spring is based on this interest.

However, my experience with agile software development has been mostly theoretical and self-taught.  An externship at Atomic Object will give me a practical view of agile software development which I can learn from actual practitioners.  A better balanced education will strengthen both my theoretical research and my teaching in the obvious ways.

The externship will also strengthen me as an advisor.  I am a good advisor for students who intend to go to graduate school since that is what I am most familiar with; I am an adequate advisor for students who go directly into the business world since I have only observational experience of the business world.  I would like to be a good (or great) advisor for both sets of students, and this externship can and will play an important role in achieving this goal.

\section*{Benefits to the College}

Agile software development is playing a larger and larger role in Computer Science these days, and few of us in the CS Department have training in this area.  While it is not necessary for all of us to be agile developers, it is appropriate that several of us do have some knowledge and experience in this area.  We need to be able to teach it to our students.

Another benefit to the department and college is establishing another relationship with a local business.  Atomic Object employed one of our graduates; a current student works there now.  It would benefit us to strengthen this relationship.

Also, if I am correct that agile software development may hold some pedagogical answers, then it will make our department stronger to take advantage of this opportunities.

\section*{Benefits to the Firm}

Atomic Object has two project planned for~2006; it is likely that they will get more by the fall.  Carl Erickson is eager for good employees.

More importantly, though, Erickson is very eager to establish Atomic Object in the Grand Rapids community.  The ties created between Atomic Object and Calvin College work both ways, and I know Erickson sees this externship as part of strengthening the firm's position in the community.

\end{document}

