\documentclass{article}

\usepackage{fullpage}
\pagestyle{empty}

\setlength{\parindent}{0in}

\begin{document}

\centerline{\Large\sc Jeremy David Frens}

\medskip

\hfill
\begin{minipage}[t]{2in}
Computer Science Department \\
Calvin College              \\
Grand Rapids, MI 49546      \\
616-957-8666                \\
jdfrens@calvin.edu          \\
\end{minipage}
\hfill
\begin{minipage}[t]{2in}
2720 Harbor Dr. \#304      \\
Kentwood, MI 49512         \\
616-455-6977               \\
jdfrens@acm.org             \\
\end{minipage}
\hfill

\section*{Education}

\parbox[t]{1in}{Indiana \\ University \\ (Bloomington)}
\hfill\begin{minipage}[t]{5.5in}
  Ph.D. expected August 1998 \\
  \textit{Matrix Factorization Using a Block-Recursive Structure and Block-Recursive Algorithms}
\end{minipage}

\smallskip
Indiana University (Bloomington) 

\hfill\begin{minipage}[t]{6.5in}
  M.S. in Computer Science (1994)
\end{minipage}

\smallskip
Calvin College (Grand Rapids, MI)

\hfill\begin{minipage}[t]{6.5in}
  B.A. in Mathematics and Computer Science (1992)
\end{minipage}

\section*{Experience}

\parbox[t]{1in}{Summer 1994.}
\hfill\parbox[t]{5.5in} {
  \textbf{Instructor}, Computer Science Department, Indiana University, Bloomington. \\
  Served as the instructor for the computer introductory course
  for non-majors; responsibilities included writing and delivering
  lectures, writing assignments and exams, managing the computer
  labs.}

\parbox[t]{1in}{Summer 1996.}
\hfill\parbox[t]{5.5in} {
  \textbf{Instructor}, Computer Science Department, Indiana University, Bloomington. \\
  Served as the instructor for the junior-level data structures
  course; responsibilities included writing and delivering lectures,
  writing assignments and exams.}

\parbox[t]{1in}{Summer 1997.}
\hfill\parbox[t]{5.5in} {
  \textbf{Instructor}, Computer Science Department, Indiana University, Bloomington. \\
  Served as the instructor for the second-semester programming course;
  this was the first time the course had been taught in Java;
  responsibilities included writing and delivering lectures, writing
  assignments and exams, managing the computer labs.}

\smallskip

\parbox[t]{1in}{\sloppy Fall 1992 \\ through present.}
\hfill\parbox[t]{5.5in}{
  \textbf{Associate Instructor}, Computer Science Department, Indiana University, Bloomington.  \\
  Each semester (Fall and Spring) and two summer sessions assisted
  with a class; responsibilities included leading discussion sections,
  preparing and grading assignments and exams, holding office hours.}

\smallskip

\parbox[t]{1in}{January 1989 \\ through \\ May 1992.}
\hfill\parbox[t]{6.5in} {
  \textbf{Hotline Operator}, Computer Center \\
  Calvin College, Grand Rapids, MI. \\
  Responsible for assisting computer users on campus with their
  computer problems.}

\section*{Publications}

\hangindent=0.25in \hangafter=1 Auto-blocking matrix-multiplication,
or Tracking BLAS3 performance from source code. \textit{Proc. 1997 ACM
  Symp. on Principles and Practice of Parallel Programming\nocorr},
\textit{ACM SIGPLAN Notices} \textbf{32}, 7, (July 1997) 206-216.
With D. Wise.
 
\smallskip
\hangindent=0.25in \hangafter=1
A new serialization for Haskell arrays.  Computer Science
Department, Indiana University (November 1996).  With D. Wise.

\smallskip
\hangindent=0.25in \hangafter=1
Matrix inversion Using quadtrees implemented in Gofer.
Technical Report 433, Computer Science Department, Indiana University
(May 1995).  With D. Wise.

% \section*{References}

% David S. Wise.  Professor of Computer Science, Indiana University
% (Bloomington).

% Dennis Gannon.  Professor and Chair of Computer Science, Indiana
% University (Bloomington).

% George Springer.  Professor Emeritus of Computer Science, Indiana
% University (Bloomington).

% David A. Bremer.  Pastor of United Presbyterian Church, Bloomington,
% IN.

\end{document}
